Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-05-23 eg6-letters/incoherent/incoherent_prl.tex
fixing typos

experimentally, $a_{lu}$ is defined as
\begin{equation}
   a_{lu} = \frac{1}{p_{b}(1-c)} \frac{n^{+} - n^{-}}{n^{+} + n^{-} },
\end{equation}
where $n^{+}$ and $n^{-}$ are the number of dvcs events for the positive and 
negative beam-helicity states, $p_{b}$ is the longitudinal beam polarization, 
and C stands for the contamination percentage of the accidental coincidences.

>>>>

Experimentally, $A_{LU}$ is defined as
\begin{equation}
   A_{LU} = \frac{1}{P_{B}(1-C)} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
negative beam-helicity states, $P_{B}$ is the longitudinal beam polarization, 
and C stands for the contamination percentage of the accidental coincidences.
